Paper 1 Analysis

### 2016-06-16 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Now 1000 resamples for alpha graph.

  scale_alpha_manual(
    name = "",
    values = c(.3, 1),
    guide = FALSE) +
  scale_color_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c("black", "black", "gray70")) +
  scale_size_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values = c(.3, .9),
    guide = FALSE) +
  scale_linetype_manual( 
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c(2,3,1)) +

@@

ggplot(mapping = aes_string(x = "delta_1_plot")) +
  geom_density(data = Rho_1_PT_data %>% filter(method != "orig")) +
  geom_point(data = Rho_1_PT_data %>% filter(method == "orig"), aes(y = 0), shape = 4, size = 3) +
  scale_x_log10(limits = c(1e-20, 1), breaks = c(1e-20, 1e-15, 1e-10, 1e-5, 1), labels=fancy_scientific) +
  xlab(expression("1 - "*delta[1])) +
  xy_theme() %>%
  graph_text_size_style(graph_text_size)

>>>>

  scale_alpha_manual(
    name = "",
    values = c(.3, 1),
    guide = FALSE) +
  scale_color_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c("black", "black", "gray70")) +
  scale_size_manual(
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values = c(0.05, 0.9),
    guide = FALSE) +
  scale_linetype_manual( 
    name = "",
    labels = c(expression(alpha[k]), expression(alpha[l]), expression(alpha[e])),
    values=c(2,3,1)) +

@@

ggplot(mapping = aes_string(x = "delta_1_plot")) +
  stat_density(data = Rho_1_PT_data %>% filter(method != "orig"), geom = "line") +
  geom_point(data = Rho_1_PT_data %>% filter(method == "orig"), aes(y = 0), shape = 4, size = 3) +
  geom_hline(aes(yintercept = 0.0), colour="gray50", size=0.1) + 
  scale_x_log10(limits = c(1e-20, 1), breaks = c(1e-20, 1e-15, 1e-10, 1e-5, 1), labels=fancy_scientific) +
  xlab(expression("1 - "*delta[1])) +
  xy_theme() %>%
  graph_text_size_style(graph_text_size)
